### 2019-07-25 figures/approach/typescript-declaration-files-generation-method/typescriptDeclarationFilesGenerationMethodBlockDiagram.tex
Add blacklisted modules figure
Add textwidth to size of figures

\begin{figure}[t]
\begin{centering}
    {\includegraphics[scale=0.9]{figures/approach/typescript_declaration_files_generation_method_block_diagram.pdf}}
    \caption[TypeScript Declaration Files Generation Method]{\textbf{TypeScript Declaration Files Generation Method} - Initial code base is retrieved from the npm package's repository. A valid TypeScript Declaration File is generated using run-time information. A Symbolic Execution Engine creates test cases based on the generated Declaration File and via a feedback loop enriches the code base until the stopping criteria is reached. The final TypeScript Declaration File gets returned.}
    \label{fig:tsd_generation_method_block_diagram}
\end{centering}
\end{figure}

>>>>

\begin{figure}[h]
\begin{centering}
    {\includegraphics[width=0.9\textwidth]{figures/approach/typescript-declaration-files-generation-method/typescript_declaration_files_generation_method_block_diagram.pdf}}
    \caption[TypeScript Declaration Files Generation Method]{\textbf{TypeScript Declaration Files Generation Method} - Initial code base is retrieved from the npm package's repository. A valid TypeScript Declaration File is generated using run-time information. A Symbolic Execution Engine creates test cases based on the generated Declaration File and via a feedback loop enriches the code base until the stopping criteria is reached. The final TypeScript Declaration File gets returned.}
    \label{fig:tsd_generation_method_block_diagram}
\end{centering}
\end{figure}
